Fig 2

### 2020-08-26 analysis/figure-2.Rmd
not working, trying to add more comparisons with labels

DEGreplace <- allDEG %>% 
  filter(comparison %in% comparisonlevelsreplace) %>%
  mutate(comparison = factor(comparison, levels = comparisonlevelsreplace)) %>%
  mutate(updown = ifelse(lfc > 0, 1, -1)) %>%
  group_by(sex, tissue, comparison, direction, label, updown) %>%
  summarise(n = n()) %>%
  mutate(n = n*updown ) %>%
  select(-updown)
DEGreplace
```

@@

b <- makebargraphv3(DEGcontrol, "hypothalamus","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages") +
  geom_rect(mapping=aes(xmin=0.5, xmax=1.5, ymin=-1000, ymax = 350, fill = F), color="black", alpha=0.5) +
  annotate("text", x = 1, y = -1075, label = "D", size = 2.5)

@@

@@

b <- makebargraphv3(DEGcontrol, "pituitary","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages")

@@

b <- makebargraphv3(DEGcontrol, "gonad","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages")

c <- makebargraphv3(DEGbldg, "gonad", "No. of DEGs\n (-)decreased  increased (+)", comparisonlabelsbldg) +
  labs(x = "Nest-building versus all other parental stages")
d <- makebargraphv3(DEGchar, "gonad", NULL,  comparisonlabelscharnobldg) +
  labs(x = "Comparison of sequential parental stages")

e <- makebargraphv3(DEGremove, "gonad", "No. of DEGs\n (-)decreased  increased (+)", comparisonlevelsremoval) +
  labs(x = "Offspring removal versus temporal control")
f <- makebargraphv3(DEGreplace, "gonad", NULL,  comparisonlablelssreplace) +
  labs(x = "Offspring removal versus temporal or external control")

>>>>

DEGreplace <- allDEG %>% 
  filter(comparison %in% comparisonlevelsreplace) %>%
  mutate(comparison = factor(comparison, levels = comparisonlevelsreplace)) %>%
  mutate(updown = ifelse(lfc > 0, 1, -1)) %>%
  group_by(sex, tissue, comparison, direction, label, updown) %>%
  summarise(n = n()) %>%
  mutate(n = n*updown ) %>%
  select(-updown)
DEGreplace

DEGcontrolreplace <- allDEG %>% 
  filter(comparison %in% comparisonlevelscontrolreplace)  %>%
  mutate(comparison = factor(comparison, levels = comparisonlevelscontrolreplace)) %>%
  mutate(updown = ifelse(lfc > 0, 1, -1)) %>%
  group_by(sex, tissue, comparison, direction, label, updown) %>%
  summarise(n = n()) %>%
  mutate(n = n*updown ) %>%
  select(-updown)

@@

b <- makebargraphv3(DEGcontrolreplace, "hypothalamus","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrolreaplce) +
  labs(x = "Control versus all other reproductive and parental stages") +
  geom_rect(mapping=aes(xmin=0.5, xmax=1.5, ymin=-1000, ymax = 350, fill = F), color="black", alpha=0.5) +
  annotate("text", x = 1, y = -1075, label = "D", size = 2.5)

@@

ab <- plot_grid(a,b,rel_widths = c(1,3), 
                labels = c("C", "D"), label_size = 8, hjust = 0)

@@

b <- makebargraphv3(DEGcontrolreplace, "pituitary","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrolreaplce) +
  labs(x = "Control versus all other reproductive and parental stages")

@@

b <- makebargraphv3(DEGcontrolreplace, "gonad","No. of DEGs\n(-) decreased  increased (+)", comparisonlevelscontrolreplace, comparisonlevelscontrolreplace) +
  labs(x = "Control versus all other reproductive and parental stages")

c <- makebargraphv3(DEGbldg, "gonad", "No. of DEGs\n (-)decreased  increased (+)", comparisonlevelsbldg, comparisonlabelsbldg) +
  labs(x = "Nest-building versus all other parental stages")
d <- makebargraphv3(DEGchar, "gonad", NULL,  comparisonlevelscharnobldg, comparisonlabelscharnobldg) +
  labs(x = "Comparison of sequential parental stages")

e <- makebargraphv3(DEGremove, "gonad", "No. of DEGs\n (-)decreased  increased (+)", comparisonlevelsremoval, comparisonlevelsremoval) +
  labs(x = "Offspring removal versus temporal control")
f <- makebargraphv3(DEGreplace, "gonad", NULL,  comparisonlevelsreplace, comparisonlablelssreplace) +
  labs(x = "Offspring removal versus temporal or external control")
